---
title: "Interactive Rio de Janeiro Health Map"
author: "Alex Curtis"
date: "July 7, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Mapping Health in Rio

This is an interactive map displaying the health establishments in Rio de Janeiro. The data was made available at http://data.rio/, which is an open data portal created by the City of Rio de Janeiro. The original dataset was coded by many factors, including neighborhood. I used the neighborhood factor to iterate a series of individual neighborhood maps, also in R. The original report on this analysis can be found here:

https://medium.com/@imcurtis/mapping-health-in-rio-de-janeiro-120d19d1b4e4

I've plotted the geographic points that these establishments are located in, and provided a popup for each, including the following markers: Neighborhood, Establishment Name, Street, Phone and Establishment Type.

```{r map}
install.packages("leaflet", repos="http://cran.us.r-project.org")
library(leaflet)
library(htmlwidgets)

health_small <- read.csv("health_small_1.csv")

m <- leaflet(health_small) %>% setView(lng=-43.4303, lat=-22.8763, zoom = 10) %>%
  addTiles() %>%  # Add default OpenStreetMap map tiles
  addMarkers(lng=-43.1729, lat=-22.9068, popup="Rio de Janeiro") %>%
  addCircles(~lon, ~lat, popup=paste("Neighbohood:", health_small$Bairro, "<br>",
                                     "Name:", health_small$NomeDeFantasia, "<br>",
                                     "Street:", health_small$logradouro, "<br>",
                                     "Phone:", health_small$Telefone, "<br>",
                                     "Establishment Type:", health_small$TipoDeEstablecimento,"<br>"), 
             weight=3, radius=40,
             color="#FF4500", stroke = TRUE, fillOpacity = 0.8)
  saveWidget(m, file="map1.html", selfcontained=FALSE)

```
## Map
```{r}
m  # Print the map
```
